Human capital mediates natural selection in contemporary humans

### 2021-07-26 why-natural-selection.Rmd
speed up res_income by not repeatedly filtering on kids_ss; tweak explanation of within-siblings results

One interpretation of these results is that natural selection on polygenic
scores is driven by their correlation with human capital, which affects
fertility as our model describes. This does not necessarily imply that polygenic
scores are causal of either human capital or fertility. Instead they may simply
correlate with different family environments, for example via "genetic nurture"
effects [@kong2018nature] or population stratification. To test whether
polygenic scores cause fertility, we estimate equation \@ref(eq:regression)
among full siblings, controlling for a full set of sibling group dummies
(Appendix Figure \@ref(fig:plot-res-fe-fertility)). All within-sibling effects
are insignificant after Bonferroni correction. Effect sizes are positively
correlated with effect sizes from the pooled model, and about 1/3 smaller
(regressing within-sibling on pooled effect sizes, b = `r coef_pool_w`, se = 
`r se_pool_w` ). Thus, there is only weak evidence that polygenic scores are
causally linked to fertility, and selection effects are at least partially
driven by gene-environment correlation. Also, if we add a control for education 
to the within-sibling regressions, effect sizes barely change. This
suggests that our measure of education only mediates differences in fertility
between sibling groups; among siblings, other causal channels are more
important.

>>>>

One interpretation of these results is that natural selection on polygenic
scores is driven by their correlation with human capital, which affects
fertility as our model describes. This does not necessarily imply that polygenic
scores are causal of either human capital or fertility. Instead they may simply
correlate with different family environments, for example via "genetic nurture"
effects [@kong2018nature] or population stratification. To test whether
polygenic scores cause fertility, we estimate equation \@ref(eq:regression)
among full siblings, controlling for a full set of sibling group dummies
(Appendix Figure \@ref(fig:plot-res-fe-fertility)). On the one hand, all 
within-sibling effects are insignificant after Bonferroni correction. On the
other hand, effect sizes are positively correlated with effect sizes from the
pooled model, and about 1/3 smaller (regressing within-sibling on pooled effect
sizes, b = `r coef_pool_w`, se = `r se_pool_w` ). We view this as providing weak
evidence that polygenic scores are causally linked to fertility, with at least
some role for correlated environments. Also, if we add a control for education
to the within-sibling regressions, effect sizes barely change. This suggests
that our measure of education only mediates differences in fertility between
sibling groups; among siblings, other causal channels are more important.
